\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb} %Use of therefore symbol
\usepackage{hyperref}
\usepackage{caption}



\begin{document}
\title{Lab 1: Monte Carlo Methods}
\author{Alex Matheson, Austin Nguyen}
%\affiliation{Department of Physics and Astronomy, University of Calgary, Calgary AB T2N 1N4 Canada}
\date{\today}
\maketitle

\section{Introduction}

\section{Methods}
\subsection{Random Numbers}


\subsection{Light Diffusion}
A number of equations were provided for different parameters in a light diffusion scenario. In this scenario, a photon enters a uniform slab and interacts with matter inside. The possible interactions are absorption, scattering, or exiting the medium. To simulate the path of a single photon through the slab, each parameter in the equations need to be randomly sampled. These parameters are not necessarily uniform. First, a sampling equation for optical depth was determined:
\begin{equation}
\begin{split}
P(\tau) d\tau =& e^{-\tau} d\tau \\
\therefore F_{\tau}(\tau) =& e^{-\tau} \\
\tau =& F^{-1}_{\tau}(u) \\
\tau =& e^{u}
\end{split}
\end{equation}

Next, the distribution for initial orientation $\theta$ was provided. From this random samples could be determined:
\begin{equation}
\begin{split}
P(\theta) d\theta =& \frac{1}{2} \sin(\theta) \\
\therefore F_{\theta}(\theta) =& \frac{1}{2} \sin(\theta)\\
\theta =& F^{-1}_{\theta}(u) \\
\theta =& \sin^{-1}(2u)
\end{split}
\end{equation}

Lastly, angle $\phi$ needed to be considered. Thankfully, this variable was already uniform.

The length travelled through the medium was dependent on the optical depth.
\begin{equation}
\begin{split}
L =& \int_{0}^{\tau_{max}}\sigma n dz \\
\end{split}
\end{equation}

For most of the path of a photon, the exit condition will not be in play. For the rest of the medium, the probability of a photon being scattered is:
\begin{equation}
prob = \frac{P_s}{P_s + P_a}
\end{equation}

Since the two probabilities must add together to $1$, the absorb or scatter condition has value $1$ associated with complete scattering (when $P_s = 1$ and $P_a=0$) or value $0$ for complete absorption (when $P_s = 0$ and $P_a=1$).

\subsection{Annealing}
In an annealing procedure, the acceptance probability of completing a change after a proposed step forward is modified by a temperature $T$. The acceptance is now defined as:
$A(x_n \to x^*) = Min \Bigg( 1, \Big( \frac{P(x^*)}{P(x_n)}\Big) ^{ \frac{1}{T(n)} } \Bigg)$
When $T=1$, the algorithm that is recovered is a simple metropolis algorithm. 

In a hyporthetical scenario, the probability term is set to 0.5 and $T=100$ initially, yielding acceptance of $0.93$. After some time, $T=1$ and the acceptance reduces to $0.5$. After still more time, $T=0.1$ and the acceptance is $0.000977$. Because of the inverse nature of $T$ in the exponent, a reduction in $T$ makes a change exponentially less likely to occur. This is typically desirable when using annealing. Ideally, the random walker being used by the algorithm is able to escape local maxima and jump to other peaks in the region early on. As time goes on, the algorithm should lower the acceptance so that it hones in on the actual peak.

%Seek clarification on e^-E question

\section{Discussion}


\section{Conclusion}

\begin{thebibliography}{00}
	\bibitem{ouyed}
	Ouyed and Dobler, PHYS 581 course notes, Department of Physics and Astrophysics, University of Calgary (2016).
	\bibitem{NR}
	W. Press et al., \emph{Numerical Recipes} (Cambridge University Press, 2010) 2nd. Ed.
\end{thebibliography}

\section{Appendix}

	
\end{document}